% !TeX root = ../thuthesis-example.tex

% 中英文摘要和关键字

\begin{abstract}
硕士论文摘要的字数一般为500字左右，博士论文摘要的字数为800--1000 字。
内容包括研究工作目的意义、 研究方法、所取得的结果和结论，应突出本论文的创造性成果或新见解，语言精炼。
英文摘要的内容应与中文摘要相对应，要符合英语语法，语句通顺，文字流畅。
中、英文摘要均应列出关键词，关键词是为了便于文献标引， 从该学位论文中选取出来用以表示全文主题内容信息款目的单词或术语，一般选取3至8个，关键词之间用顿号分隔。
  
    \hdusetup{
        keywords = {关键词1、 关键词2、 关键词3、 关键词4、 关键词5},
    }
\end{abstract}

\begin{abstract*}
  An abstract of a dissertation is a summary and extraction of research work and contributions.
  Included in an abstract should be description of research topic and research objective, brief introduction to methodology and research process, and summary of conclusion and contributions of the research.
  An abstract should be characterized by independence and clarity and carry identical information with the dissertation.
  It should be such that the general idea and major contributions of the dissertation are conveyed without reading the dissertation.

  An abstract should be concise and to the point.
  It is a misunderstanding to make an abstract an outline of the dissertation and words “the first chapter”, “the second chapter” and the like should be avoided in the abstract.

  Keywords are terms used in a dissertation for indexing, reflecting core information of the dissertation.
  An abstract may contain a maximum of 5 keywords, with semi-colons used in between to separate one another.

  % Use comma as separator when inputting
    \hdusetup{
        keywords* = {keyword 1, keyword 2, keyword 3, keyword 4, keyword 5},
    }
\end{abstract*}
